Automated Classification of TA Comments on Student Writing

### 2019-05-13 build.Rmd
update

####Extracting TAs' Comments 
*(Preliminary coding)*  
Fully R-based protocol for extracting TA comments from student lab reports. Will replace current process using a mix of Linux and Excel scripts.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

####Structure of Development Dataset; Data Import & Validation 
*(Complete)*  
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

####Codebook for Classifying TAs' Comments 
*(Complete)*  
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

####Initial Exploration of Dataset 
*(Partly complete)*  
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

####Naive Bayes Comment Classifier 
*(Complete)*  
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

####Embedding Naive Bayes Classifier in an Ensemble Model  
*(Initial design stage)*
Outlines a strategy for combining pattern matching and other pre-processing steps with Naive Bayes Classifier to improve accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

>>>>

####Extracting TAs' Comments 
*(Draft)*  
Fully R-based protocol for extracting TA comments from student lab reports. Will replace current process using a mix of Linux and Excel scripts.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

####Structure of Development Dataset; Data Import & Validation 
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

####Codebook for Classifying TAs' Comments 
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

####Initial Exploration of Dataset 
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

####Naive Bayes Comment Classifier 
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

####Embedding Naive Bayes Classifier in an Ensemble Model  
Outlines a strategy for combining pattern matching and other pre-processing steps with Naive Bayes Classifier to improve accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

### 2019-05-13 docxcommentextraction.Rmd
update

---
title: "DOCX Comment Extraction"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The testing dataset used in this project was created using BaSH scripting and one-off tools. This page documents progress on a workflow to replicate that process using R tools.

@@

#General Approach
Create a list of files to cycle through OR put all files to process in ONE folder. For each file, use 'read_docx', then 'docx_extract_all_cmnts'. Use 'do.call("rbind", list(dataframes to merge))' to cycle through and append the extracted comments to ONE dataframe

>>>>

---
title: "DRAFT: DOCX Comment Extraction"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The testing dataset used in this project was created using BaSH scripting and one-off text processing. This page documents progress on building a workflow to replicate that process using R tools.

@@

#General Approach
*  Create a list of files to cycle through OR put all files to process in ONE folder. 
*  For each file, use 'read_docx', then 'docx_extract_all_cmnts'. 
*  Use 'do.call("rbind", list(dataframes to merge))' to cycle through and append the extracted comments to ONE dataframe

### 2019-05-13 index.Rmd
update

##Project Site Map
Insert a text-based overview and site map of the major pages and branch points here.

When appropriate, anchor pages branch to extended supporting documentation.

>>>>

##Project Site Map
![](/Users/danjohnson/Dropbox/Coding_Tools/R_Environment/R_Projects/default_website/images/Sitemap.png)
